---
title: "Utlity Linking Model"
output: html_notebook
---

All models are Mixed Integer Programs that are coded and ran with Gurobi 8.1.1

```{r}
library(gurobi)
library(tictoc)
library(Matrix)
#library(FinCal)
library(readxl)
library(tidyverse)
```

These R codes bring in capacity factors for wind and solar from ERCOT and Pecan Street respectively. This code also brings in the demand profile data from Pecan Street as well for 30 single family homes in the Mueller neighborhood in Austin, Texas. The demand profile is given as a fraction for each time slice and will be multiplied by a demand number

```{r}
library(readxl)

#These files included that are commented out are not included due to licensing requirements from Pecan Street
#the needed required objects are in the Rdata file

#load("~/Coding/R/decomp_sol_df.RData")

filename <- 'indata1.xlsx'
demand.kwh.raw <- read_excel(filename, sheet='Demand_kWh', col_names = FALSE)
capacity.factor.raw <- read_excel(filename, sheet='CapacityFactor', col_names = FALSE)
demand.kwh.raw1 <- as.data.frame(demand.kwh.raw[-c(1:7),-c(1:2,15:16)], stringsasfactor = FALSE, col.names = NULL)
demand.kwh.raw1[] <- lapply(demand.kwh.raw1,function(x) as.numeric(as.character(x)))





#removing values by month length
#demand.kwh.raw1[745:nrow(demand.kwh.raw1),c(1,3,5,7,8,10,12)] <- NA
demand.kwh.raw1[721:nrow(demand.kwh.raw1),c(4,6,9,11)] <- NA
demand.kwh.raw1[673:nrow(demand.kwh.raw1),2] <- NA

#length(which(is.na(demand.kwh.raw1)==TRUE))
demand.kwh <- unlist(demand.kwh.raw1)
demand.kwh <- demand.kwh[!is.na(demand.kwh)]
demand.kwh <- demand.kwh / sum(demand.kwh)

tail(demand.kwh.raw1,15)
head(demand.kwh)

rm(demand.kwh.raw,demand.kwh.raw1,filename)
```

This R Code calculates the capacity factors for solar, wind, and NG

```{r}
#Capacity factor for Solar

capacity.factor.solar.raw <- as.data.frame(capacity.factor.raw[-c(1:9,745+9:nrow(capacity.factor.raw)),-c(1:2,15:19)])
capacity.factor.solar.raw[] <- lapply(capacity.factor.solar.raw, function(x) as.numeric(as.character(x)))

#capacity.factor.solar.raw[745:nrow(capacity.factor.solar.raw),c(1,3,5,7,8,10,12)] <- NA
capacity.factor.solar.raw[721:nrow(capacity.factor.solar.raw),c(4,6,9,11)] <- NA
capacity.factor.solar.raw[673:nrow(capacity.factor.solar.raw),2] <- NA
 
 
#length(which(is.na(capacity.factor.solar.raw)==TRUE))
capacity.factor.solar <- unlist(capacity.factor.solar.raw)
capacity.factor.solar <- capacity.factor.solar[!is.na(capacity.factor.solar)]

#Additional capacity factor because industrial solar panels are more efficient than household ones and then a normalization factor
com.eff.improve <- 0.10
capacity.factor.solar <- capacity.factor.solar + com.eff.improve
for(i in 1:length(capacity.factor.solar)){
  if(capacity.factor.solar[i] <=(0.009 + com.eff.improve)){
    capacity.factor.solar[i] <- capacity.factor.solar[i] - com.eff.improve
  }
  if(capacity.factor.solar[i] >= 1){
    capacity.factor.solar[i] <- capacity.factor.solar[i] - com.eff.improve
  }
  
}

#Capacity factor for Wind
capacity.factor.wind.raw <- as.data.frame(capacity.factor.raw[-c(1:754),-c(1:2,15:19)])
capacity.factor.wind.raw[] <- lapply(capacity.factor.wind.raw, function(x) as.numeric(as.character(x)))
#capacity.factor.wind.raw[745:nrow(capacity.factor.wind.raw),c(1,3,5,7,8,10,12)] <- NA
capacity.factor.wind.raw[721:nrow(capacity.factor.wind.raw),c(4,6,9,11)] <- NA
capacity.factor.wind.raw[673:nrow(capacity.factor.wind.raw),2] <- NA
#length(which(is.na(capacity.factor.wind.raw)==TRUE))
capacity.factor.wind <- unlist(capacity.factor.wind.raw)
capacity.factor.wind <- capacity.factor.wind[!is.na(capacity.factor.wind)]



#Capacity Factor for NG

capacity.factor.ng <- rep(.87,8760)


# head(capacity.factor.raw,15)
# head(capacity.factor.solar)
# head(capacity.factor.wind)
mean(capacity.factor.ng)
mean(capacity.factor.solar)
mean(capacity.factor.wind)


rm(capacity.factor.raw,capacity.factor.solar.raw,capacity.factor.wind.raw,i,com.eff.improve)

```

This code codes the A variables of the constraints. C1 creates the equation Prod_ELC >= Demand*DemandProfile

```{r}


nTimePeriods <- 24*365
Technologies <- c('NG','Solar', 'Wind')
nTechnologies <- length(Technologies)

#Matrix is defined as NG(timeperiod = 1),...NG(timeperiod = 24*365),Solar(timeperiod = 1), ..., Solar(timeperiod = 24*365), Wind(timeperiod = 1),..., Wind(timperiod = 24*365), NG(investment),Solar(investment),Wind(investment)
#Combines all of the capacity factors multiplied by the Capacity of one unit of technolgy in one vector

CF <- c(capacity.factor.ng[1:nTimePeriods]*25000,capacity.factor.solar[1:nTimePeriods]*500,capacity.factor.wind[1:nTimePeriods]*1000)

C1   <- spMatrix(nTimePeriods, (nTimePeriods*nTechnologies+3),
               i = c(rep(1:nTimePeriods,nTechnologies)),
               j = c(1:(nTimePeriods*nTechnologies)),
               x = c(rep(1,(nTimePeriods*nTechnologies))))
C2a <- .sparseDiagonal((nTimePeriods*nTechnologies),1)
C2b <- spMatrix((nTimePeriods*nTechnologies),3,
                i = c(1:(nTimePeriods*nTechnologies)),
                j = c(mapply(rep,(1:nTechnologies),nTimePeriods)),
                x = c(-CF)  )

C2 <- cbind(C2a,C2b)

# object.size(C1)
# object.size(C2)
nrow(C1)
ncol(C1)
nrow(C2)
ncol(C2)

rm(Technologies)
```


The unit sizes of the natural gas combined cycle, solar, and wind power plants are set at 10 MW, 1 MW, and 1 MW respectively. The capital investments are set as integer variables and investments must be done in these increments.

The R code below transforms the CAPEX cost into an annutity with a discount rate of 5% and payback period of 10 years. Since the costs are annuitized the fixed O&M is simply added to the annutized CAPEX cost giving one annual cost for all the technolgy investments given in the units $/unit.  

The variable costs for each technology which includes variable O&M and fuel costs are added together and transformed into the units $/kWh.

```{r}
library(FinCal)

nTimePeriods <- 8760
cost.td <- 0.03
discount_rate <- 0.05
payback_period <- 20

cost.df1 <- data.frame(NG = c(21,3,927,11,25,0.87), Solar = c(0,0,1096,20,0.5,0.26), Wind = c(0,0,1610,44,1,0.36))
rownames(cost.df1) <- c('Fuel Cost $/MWh','Variable O&M $/MWh', 'CAPEX $/kW', 'Fixed O&M $/kW-yr','Capacity MW/unit','Mean Capacity Factor')
cost.df <- cost.df1[1:4,]
cost.df
cost.df.print <- as.data.frame(as.matrix(t(cost.df1)))

cost.annual.NG <- -(pmt(discount_rate,payback_period, pv = cost.df[3,1], fv = 0)+cost.df[4,1])*25000
cost.annual.Solar <- -(pmt(discount_rate,payback_period, pv = cost.df[3,2], fv = 0)+cost.df[4,2])*500
cost.annual.Wind <- -(pmt(discount_rate,payback_period, pv = cost.df[3,3], fv = 0)+cost.df[4,3])*1000

cost.variable.NG <- (cost.df[1,1]+cost.df[2,1])/1000
cost.variable.Solar <- (cost.df[1,2]+cost.df[2,2])/500
cost.variable.Wind <- (cost.df[1,3]+cost.df[2,3])/1000

cost <- c(rep(cost.variable.NG+cost.td,nTimePeriods), rep(cost.variable.Solar+cost.td,nTimePeriods), rep(cost.variable.Wind+cost.td,nTimePeriods), cost.annual.NG, cost.annual.Solar, cost.annual.Wind)


# print(paste('Cost of 1 MWh of Solar:', format(round(cost.annual.Solar/mean(capacity.factor.solar))+cost.variable.Solar*1000,big.mark=',',scientific = FALSE)))
# print(paste('Cost of 1 MWh of Wind:', format(round(cost.annual.Wind/mean(capacity.factor.wind))+cost.variable.Wind*1000,big.mark=',',scientific = FALSE)))
# print(paste('Cost of 10 MWh of NG:', format(cost.annual.NG/mean(capacity.factor.ng)+cost.variable.NG*10000/mean(capacity.factor.ng),big.mark=',',scientific = FALSE)))




```

The R code below builds the model. First it calculates the RHS for the problem from a given annual demand, the demand data gathered previously, and the RHS from the capacity constraints. Then it combines the A matrix and cost data from above.

```{r}
library(gurobi)

#Say 250 houses 6000 kWh a year (500 kWh/month/house), assume same for commericial ~3,000,000 kWh per community
#40 communities for 10,000 homes 120,000 MWh of demand a year or 120,000,000 kWh
demand.annual <- 3000000*40

RHS <- c((demand.annual*demand.kwh[1:nTimePeriods]),rep(0,nrow(C2)))


# Build model
model     <- list()
#spMatrix tells you where to put the non zero values in matrix i,j is the location and x are teh values for each pair
model$A   <- rbind(C1,C2)
model$obj         <- cost
#model$lb          <- c(rep(0,(nTimePeriods*nTechnologies)),0,1,1)
#model$ub          <- 100000
#model$varnames <- c(paste0(rep('Open',nPlants),1:nPlants),                    sprintf('Trans%d,%d',                            c(mapply(rep,1:nWarehouses,nPlants)),                            1:nPlants))
model$vtype    <- c(rep('C', (nTimePeriods*nTechnologies)), rep('I', 3))
model$rhs         <- RHS
model$sense       <- c(rep('>=',nrow(C1)),rep('<=',nrow(C2)))
#model$constrnames <- Categories
model$modelname   <- 'Utility Electric Generation Plan'
model$modelsense  <- 'min'


#Checking

sum(demand.kwh)
model.util <- model

rm(RHS,C2a,C2b)

```

Solving the utiltity model and saving the outputs:

```{r}


sol <- gurobi(model)

early <- c()
morning <- c()
noon <- c()
afternoon <- c()
night <- c()
late <- c()

for(i in 0:364){
early <- c(early,c(1,2,3,4)+i*24) 
morning <- c(morning,c(5,6,7,8)+i*24)
noon <- c(noon,c(9,10,11,12)+i*24)
afternoon <- c(afternoon,c(13,14,15,16)+i*24)
night <- c(night,c(17,18,19,20)+i*24)
late <- c(late,c(21,22,23,24)+i*24)
}

solution.df <- data.frame(NG.early = c(sol$x[early]),NG.morning = c(sol$x[morning]), NG.noon = c(sol$x[noon]), NG.afternoon = c(sol$x[afternoon]), NG.night = c(sol$x[night]),NG.late = c(sol$x[late]), 
Solar.early = c(sol$x[(early+8760)]), Solar.morning = c(sol$x[(morning+8760)]), Solar.noon = c(sol$x[(noon+8760)]), Solar.afternoon = c(sol$x[(afternoon+8760)]), Solar.night = c(sol$x[(night+8760)]),Solar.late = c(sol$x[(late+8760)]), Wind.early = c(sol$x[(early+8760*2)]), Wind.morning = c(sol$x[(morning+8760*2)]), Wind.noon = c(sol$x[(noon+8760*2)]), Wind.afternoon = c(sol$x[(afternoon+8760*2)]), Wind.night = c(sol$x[(night+8760*2)]),Wind.late = c(sol$x[(late+8760*2)]) )

investments.df <- c(sol$x[(nTechnologies*nTimePeriods+1)],sol$x[(nTechnologies*nTimePeriods+2)],sol$x[(nTechnologies*nTimePeriods+3)])





#Tranmsission and Distribution cost $/kWh
cost.td <- 0.03

price.fraction <-  (demand.kwh*demand.annual)/(investments.df[1]*CF[1:nTimePeriods]
                                                 +investments.df[2]*CF[(nTimePeriods+1):(nTimePeriods*2)]
                                                  +investments.df[3]*CF[(nTimePeriods*2+1):(nTimePeriods*3)])

summary(price.fraction)
sum(price.fraction)


#normalizes price fraction to one and add cost.d
price.fraction <- price.fraction/sum(price.fraction) 

summary(price.fraction)
sum(price.fraction)

price.fixed <- sol$objval / demand.annual 

price.demand <- price.fraction*sol$objval/(demand.annual*(demand.kwh+0.0000001))

summary(price.demand)
mean(price.demand)
sum(price.demand*demand.kwh)
price.fixed


cost.list <- list()
solution.list <- list()
investments.list <- list()
price.demand.list <- list()

cost.list[[1]] <- sol$objval
solution.list[[1]] <- solution.df
investments.list[[1]] <- investments.df
price.demand.list[[1]] <- price.demand


investments.df
colSums(solution.df)

rm(sol,model,solution.df,investments.df,i,price.fraction,price.fixed)


```


The R code below models a community. The community decides to invest in community solar or wind based on the time of use utility prices.

```{r}
#The community model

#nTimePeriods, capacity factors and C1 are the same
Technologies <- c('Utility','Solar', 'Wind')
nTechnologies <- length(Technologies)
cost.td.com <- 0.01


#Combines all of the capacity factors multiplied by the Capacity of one unit of technolgy in one vector
#The utility has enough capacity to power any timeslice, solar is reduced to 500 MW investments, and wind stays 1MW
capacity.factor.util <- rep((demand.annual*max(demand.kwh)),nTimePeriods)

CF.com <- c(capacity.factor.util[1:nTimePeriods],capacity.factor.solar[1:nTimePeriods]*500,capacity.factor.wind[1:nTimePeriods]*1000)


C2a.com <- .sparseDiagonal((nTimePeriods*nTechnologies),1)
C2b.com <- spMatrix((nTimePeriods*nTechnologies),3,
                i = c(1:(nTimePeriods*nTechnologies)),
                j = c(mapply(rep,(1:nTechnologies),nTimePeriods)),
                x = c(-CF.com)  )
C2.com <- cbind(C2a.com,C2b.com)

#solar cost is adjusted by half and *2 utility annual cost is removed and the util variable cost is added
cost.util <- price.demand
cost.com <- c(cost.util, rep((cost.variable.Solar+cost.td.com),nTimePeriods), rep((cost.variable.Wind+cost.td.com),nTimePeriods), 0, cost.annual.Solar, cost.annual.Wind)

rm(C2b.com,C2a.com)
```

THe Community model:
```{r}
# 3,000,000 kWh per community
demand.annual <- 3000000
RHS <- c((demand.annual*demand.kwh[1:nTimePeriods]),rep(0,nrow(C2.com)))

# Build model
model     <- list()
#spMatrix tells you where to put the non zero values in matrix i,j is the location and x are teh values for each pair
model$A   <- rbind(C1,C2.com)
model$obj         <- cost.com

model$vtype    <- c(rep('C', (nTimePeriods*nTechnologies)), rep('I', 3))
model$rhs         <- RHS
model$sense       <- c(rep('>=',nrow(C1)),rep('<=',nrow(C2.com)))
#model$constrnames <- Categories
model$modelname   <- 'Community Electric Plan'
model$modelsense  <- 'min'
#suppress output
params <- list(OutputFlag = 0)
sol <- gurobi(model,params)

print('MIP Solve Status')
sol$status
print('Objective Value')
sol$objval

#rm(C1.com,C2.com,RHS)
```


```{r}
cost.list.com <- list()
solution.list.com <- list()
investments.list.com <- list()
generation.util.list.com <- list()
                                                                                                                      

solution.df.com <- data.frame(Util.early = c(sol$x[early]),Util.morning = c(sol$x[morning]), Util.noon = c(sol$x[noon]), Util.afternoon = c(sol$x[afternoon]), Util.night = c(sol$x[night]),Util.late = c(sol$x[late]), 
                              
Solar.early = c(sol$x[(early+8760)]), Solar.morning = c(sol$x[(morning+8760)]), Solar.noon = c(sol$x[(noon+8760)]), Solar.afternoon = c(sol$x[(afternoon+8760)]), Solar.night = c(sol$x[(night+8760)]),Solar.late = c(sol$x[(late+8760)]), 
Wind.early = c(sol$x[(early+8760*2)]), Wind.morning = c(sol$x[(morning+8760*2)]), Wind.noon = c(sol$x[(noon+8760*2)]), Wind.afternoon = c(sol$x[(afternoon+8760*2)]), Wind.night = c(sol$x[(night+8760*2)]),Wind.late = c(sol$x[(late+8760*2)]) )

investments.df.com <- c(sol$x[(nTechnologies*nTimePeriods+1)],sol$x[(nTechnologies*nTimePeriods+2)],sol$x[(nTechnologies*nTimePeriods+3)])



generation.util.com <- sum(colSums(solution.df.com[1:6]))


print('Yearly generation met by source and time of day')
colSums(solution.df.com)
print('Yearly generation by source')
c(sum(colSums(solution.df.com[1:6])),sum(colSums(solution.df.com[7:12])),sum(colSums(solution.df.com[13:18])))
print('Yearly generation by Utility')
generation.util.com
print('Excess Electricity Production')
sum(colSums(solution.df.com))-demand.annual
print('Investments made [Utility,Solar,Wind]')
investments.df.com

model.com <- model

solution.list.com[[1]] <- solution.df.com
investments.list.com[[1]] <- investments.df.com
generation.util.list.com[[1]] <- generation.util.com
cost.list.com[[1]] <- sol$objval
```

Calculated Prices of Community

```{r}
#Tranmsission and Distribution cost $/kWh for the community model


price.fraction.com <-  (demand.kwh*demand.annual)/(investments.df.com[2]*CF[(nTimePeriods+1):(nTimePeriods*2)] +investments.df.com[3]*CF[(nTimePeriods*2+1):(nTimePeriods*3)])




#normalizes price fraction to one and add cost.d
price.fraction.com <- price.fraction.com/sum(price.fraction.com) 

summary(price.fraction.com)
sum(price.fraction.com)

price.fixed.com <- sol$objval / demand.annual 

price.demand.com <- price.fraction.com*sol$objval/(demand.annual*(demand.kwh+0.0000001))

summary(price.demand.com)
mean(price.demand.com)
sum(price.demand.com*demand.kwh)
price.fixed.com

rm(sol,model,solution.df.com,investments.df.com,generation.util.com,price.demand.com,price.fixed.com,price.fraction.com)

```

```{r}
#iterations for 1 community
ncoms <- 1


nitrs <- 4
params <- list(OutputFlag = 0)
for(i in 2:nitrs){
  
#New utility model with new demand

model <- model.util

demand.annual <- 3000000*(40-ncoms)+ncoms*generation.util.list.com[[(i-1)]]

model$rhs   <- c((demand.annual*demand.kwh[1:nTimePeriods]),rep(0,nrow(C2)))

sol <- gurobi(model, params)

solution.df <- data.frame(NG.early = c(sol$x[early]),NG.morning = c(sol$x[morning]), NG.noon = c(sol$x[noon]), NG.afternoon = c(sol$x[afternoon]), NG.night = c(sol$x[night]),NG.late = c(sol$x[late]), 
Solar.early = c(sol$x[(early+8760)]), Solar.morning = c(sol$x[(morning+8760)]), Solar.noon = c(sol$x[(noon+8760)]), Solar.afternoon = c(sol$x[(afternoon+8760)]), Solar.night = c(sol$x[(night+8760)]),Solar.late = c(sol$x[(late+8760)]), Wind.early = c(sol$x[(early+8760*2)]), Wind.morning = c(sol$x[(morning+8760*2)]), Wind.noon = c(sol$x[(noon+8760*2)]), Wind.afternoon = c(sol$x[(afternoon+8760*2)]), Wind.night = c(sol$x[(night+8760*2)]),Wind.late = c(sol$x[(late+8760*2)]) )


investments.df <- c(sol$x[(nTechnologies*nTimePeriods+1)],sol$x[(nTechnologies*nTimePeriods+2)],sol$x[(nTechnologies*nTimePeriods+3)])


#Tranmsission and Distribution cost $/kWh
price.fraction <-  (demand.kwh*demand.annual)/(investments.df[1]*CF[1:nTimePeriods]
                                                 +investments.df[2]*CF[(nTimePeriods+1):(nTimePeriods*2)]
                                                  +investments.df[3]*CF[(nTimePeriods*2+1):(nTimePeriods*3)])

price.fraction <- price.fraction/sum(price.fraction) 
price.demand <- price.fraction*sol$objval/(demand.annual*(demand.kwh+0.0000001))

cost.list[[i]] <- sol$objval
solution.list[[i]] <- solution.df
investments.list[[i]] <- investments.df
price.demand.list[[i]] <- price.demand


print(paste('Iteration Count:', i))

rm(sol,model,solution.df,investments.df,price.demand,price.fraction)


  
#New community model with new prices
model <- model.com

model$obj <- c(price.demand.list[[(i)]], rep((cost.variable.Solar+cost.td.com),nTimePeriods), rep((cost.variable.Wind+cost.td.com),nTimePeriods), 0, cost.annual.Solar, cost.annual.Wind)
sol <- gurobi(model,params)

solution.df.com <- data.frame(Util.early = c(sol$x[early]),Util.morning = c(sol$x[morning]), Util.noon = c(sol$x[noon]), Util.afternoon = c(sol$x[afternoon]), Util.night = c(sol$x[night]),Util.late = c(sol$x[late]), 
Solar.early = c(sol$x[(early+8760)]), Solar.morning = c(sol$x[(morning+8760)]), Solar.noon = c(sol$x[(noon+8760)]), Solar.afternoon = c(sol$x[(afternoon+8760)]), Solar.night = c(sol$x[(night+8760)]),Solar.late = c(sol$x[(late+8760)]), Wind.early = c(sol$x[(early+8760*2)]), Wind.morning = c(sol$x[(morning+8760*2)]), Wind.noon = c(sol$x[(noon+8760*2)]), Wind.afternoon = c(sol$x[(afternoon+8760*2)]), Wind.night = c(sol$x[(night+8760*2)]),Wind.late = c(sol$x[(late+8760*2)]) )

investments.df.com <- c(sol$x[(nTechnologies*nTimePeriods+1)],sol$x[(nTechnologies*nTimePeriods+2)],sol$x[(nTechnologies*nTimePeriods+3)])

generation.util.com <- sum(colSums(solution.df.com[1:6]))

cost.list.com[[i]] <- sol$objval
solution.list.com[[i]] <- solution.df.com
investments.list.com[[i]] <- investments.df.com
generation.util.list.com[[i]] <- generation.util.com


rm(sol,model,solution.df.com,investments.df.com,generation.util.com)
  

}

print('Objective Values for the Utility Models' )
unlist(cost.list)
print('Objective Values for the Community Models' )
unlist(cost.list.com)
print('Total Cost Utility+Community')
unlist(cost.list)+unlist(cost.list.com)*ncoms
print('Utility Prices')
lapply(price.demand.list,mean)
print('Utility Investments')
investments.list
print('Community Investments')
investments.list.com
print('Fraction of Energy Generation by Community')
(3000000-unlist(generation.util.list.com))*ncoms/(120000000)
print('Excess Electricity Produced by Community')
max(0,ncoms*sum(colSums(solution.list.com[[i]]))-(3000000*ncoms))
print('Mean $/kWh for Community Generation')
ncoms*unlist(cost.list.com) / (3000000*ncoms) 


cost.list.1 <- cost.list
solution.list.1 <- solution.list
investments.list.1 <- investments.list
price.demand.list.1 <- price.demand.list

cost.list.com.1 <- cost.list.com
solution.list.com.1 <- solution.list.com
investments.list.com.1 <- investments.list.com


```

```{r}
#iterations for 5 communities

ncoms <- 5
params <- list(OutputFlag = 0)

  
for(i in 2:nitrs){
  
#New utility model with new demand

model <- model.util

demand.annual <- 3000000*(40-ncoms)+ncoms*generation.util.list.com[[(i-1)]]

model$rhs   <- c((demand.annual*demand.kwh[1:nTimePeriods]),rep(0,nrow(C2)))

sol <- gurobi(model, params)

solution.df <- data.frame(NG.early = c(sol$x[early]),NG.morning = c(sol$x[morning]), NG.noon = c(sol$x[noon]), NG.afternoon = c(sol$x[afternoon]), NG.night = c(sol$x[night]),NG.late = c(sol$x[late]), 
Solar.early = c(sol$x[(early+8760)]), Solar.morning = c(sol$x[(morning+8760)]), Solar.noon = c(sol$x[(noon+8760)]), Solar.afternoon = c(sol$x[(afternoon+8760)]), Solar.night = c(sol$x[(night+8760)]),Solar.late = c(sol$x[(late+8760)]), Wind.early = c(sol$x[(early+8760*2)]), Wind.morning = c(sol$x[(morning+8760*2)]), Wind.noon = c(sol$x[(noon+8760*2)]), Wind.afternoon = c(sol$x[(afternoon+8760*2)]), Wind.night = c(sol$x[(night+8760*2)]),Wind.late = c(sol$x[(late+8760*2)]) )


investments.df <- c(sol$x[(nTechnologies*nTimePeriods+1)],sol$x[(nTechnologies*nTimePeriods+2)],sol$x[(nTechnologies*nTimePeriods+3)])


#Tranmsission and Distribution cost $/kWh
price.fraction <-  (demand.kwh*demand.annual)/(investments.df[1]*CF[1:nTimePeriods]
                                                 +investments.df[2]*CF[(nTimePeriods+1):(nTimePeriods*2)]
                                                  +investments.df[3]*CF[(nTimePeriods*2+1):(nTimePeriods*3)])

price.fraction <- price.fraction/sum(price.fraction) 
price.demand <- price.fraction*sol$objval/(demand.annual*(demand.kwh+0.0000001))

cost.list[[i]] <- sol$objval
solution.list[[i]] <- solution.df
investments.list[[i]] <- investments.df
price.demand.list[[i]] <- price.demand


print(paste('Iteration Count:', i))

rm(sol,model,solution.df,investments.df,price.demand,price.fraction)


  
#New community model with new prices
model <- model.com

model$obj <- c(price.demand.list[[(i)]], rep((cost.variable.Solar+cost.td.com),nTimePeriods), rep((cost.variable.Wind+cost.td.com),nTimePeriods), 0, cost.annual.Solar, cost.annual.Wind)
sol <- gurobi(model,params)

solution.df.com <- data.frame(Util.early = c(sol$x[early]),Util.morning = c(sol$x[morning]), Util.noon = c(sol$x[noon]), Util.afternoon = c(sol$x[afternoon]), Util.night = c(sol$x[night]),Util.late = c(sol$x[late]), 
Solar.early = c(sol$x[(early+8760)]), Solar.morning = c(sol$x[(morning+8760)]), Solar.noon = c(sol$x[(noon+8760)]), Solar.afternoon = c(sol$x[(afternoon+8760)]), Solar.night = c(sol$x[(night+8760)]),Solar.late = c(sol$x[(late+8760)]), Wind.early = c(sol$x[(early+8760*2)]), Wind.morning = c(sol$x[(morning+8760*2)]), Wind.noon = c(sol$x[(noon+8760*2)]), Wind.afternoon = c(sol$x[(afternoon+8760*2)]), Wind.night = c(sol$x[(night+8760*2)]),Wind.late = c(sol$x[(late+8760*2)]) )

investments.df.com <- c(sol$x[(nTechnologies*nTimePeriods+1)],sol$x[(nTechnologies*nTimePeriods+2)],sol$x[(nTechnologies*nTimePeriods+3)])

generation.util.com <- sum(colSums(solution.df.com[1:6]))

cost.list.com[[i]] <- sol$objval
solution.list.com[[i]] <- solution.df.com
investments.list.com[[i]] <- investments.df.com
generation.util.list.com[[i]] <- generation.util.com


rm(sol,model,solution.df.com,investments.df.com,generation.util.com)
  

}


print('Objective Values for the Utility Models' )
unlist(cost.list)
print('Objective Values for the Community Models' )
unlist(cost.list.com)
print('Total Cost Utility+Community')
unlist(cost.list)+unlist(cost.list.com)*ncoms
print('Utility Prices')
lapply(price.demand.list,mean)
print('Utility Investments')
investments.list
print('Community Investments')
investments.list.com
print('Fraction of Energy Generation by Community')
(3000000-unlist(generation.util.list.com))*ncoms/(120000000)
print('Excess Electricity Produced by Community')
max(0,ncoms*sum(colSums(solution.list.com[[i]]))-(3000000*ncoms))
print('Mean $/kWh for Community Generation')
ncoms*unlist(cost.list.com) / (3000000*ncoms) 


cost.list.5 <- cost.list
solution.list.5 <- solution.list
investments.list.5 <- investments.list
price.demand.list.5 <- price.demand.list

cost.list.com.5 <- cost.list.com
solution.list.com.5 <- solution.list.com
investments.list.com.5 <- investments.list.com


```

```{r}
#iterations for 10 communities
ncoms <- 10

params <- list(OutputFlag = 0)
for(i in 2:nitrs){
  
#New utility model with new demand

model <- model.util

demand.annual <- 3000000*(40-ncoms)+ncoms*generation.util.list.com[[(i-1)]]

model$rhs   <- c((demand.annual*demand.kwh[1:nTimePeriods]),rep(0,nrow(C2)))

sol <- gurobi(model, params)

solution.df <- data.frame(NG.early = c(sol$x[early]),NG.morning = c(sol$x[morning]), NG.noon = c(sol$x[noon]), NG.afternoon = c(sol$x[afternoon]), NG.night = c(sol$x[night]),NG.late = c(sol$x[late]), 
Solar.early = c(sol$x[(early+8760)]), Solar.morning = c(sol$x[(morning+8760)]), Solar.noon = c(sol$x[(noon+8760)]), Solar.afternoon = c(sol$x[(afternoon+8760)]), Solar.night = c(sol$x[(night+8760)]),Solar.late = c(sol$x[(late+8760)]), Wind.early = c(sol$x[(early+8760*2)]), Wind.morning = c(sol$x[(morning+8760*2)]), Wind.noon = c(sol$x[(noon+8760*2)]), Wind.afternoon = c(sol$x[(afternoon+8760*2)]), Wind.night = c(sol$x[(night+8760*2)]),Wind.late = c(sol$x[(late+8760*2)]) )

investments.df <- c(sol$x[(nTechnologies*nTimePeriods+1)],sol$x[(nTechnologies*nTimePeriods+2)],sol$x[(nTechnologies*nTimePeriods+3)])



#Tranmsission and Distribution cost $/kWh
price.fraction <-  (demand.kwh*demand.annual)/(investments.df[1]*CF[1:nTimePeriods]
                                                 +investments.df[2]*CF[(nTimePeriods+1):(nTimePeriods*2)]
                                                  +investments.df[3]*CF[(nTimePeriods*2+1):(nTimePeriods*3)])

price.fraction <- price.fraction/sum(price.fraction) 
price.demand <- price.fraction*sol$objval/(demand.annual*(demand.kwh+0.0000001))

cost.list[[i]] <- sol$objval
solution.list[[i]] <- solution.df
investments.list[[i]] <- investments.df
price.demand.list[[i]] <- price.demand


print(paste('Iteration Count:', i))

rm(sol,model,solution.df,investments.df,price.demand,price.fraction)


  
#New community model with new prices
model <- model.com

model$obj <- c(price.demand.list[[(i)]], rep((cost.variable.Solar+cost.td.com),nTimePeriods), rep((cost.variable.Wind+cost.td.com),nTimePeriods), 0, cost.annual.Solar, cost.annual.Wind)
sol <- gurobi(model,params)

solution.df.com <- data.frame(Util.early = c(sol$x[early]),Util.morning = c(sol$x[morning]), Util.noon = c(sol$x[noon]), Util.afternoon = c(sol$x[afternoon]), Util.night = c(sol$x[night]),Util.late = c(sol$x[late]), 
Solar.early = c(sol$x[(early+8760)]), Solar.morning = c(sol$x[(morning+8760)]), Solar.noon = c(sol$x[(noon+8760)]), Solar.afternoon = c(sol$x[(afternoon+8760)]), Solar.night = c(sol$x[(night+8760)]),Solar.late = c(sol$x[(late+8760)]), Wind.early = c(sol$x[(early+8760*2)]), Wind.morning = c(sol$x[(morning+8760*2)]), Wind.noon = c(sol$x[(noon+8760*2)]), Wind.afternoon = c(sol$x[(afternoon+8760*2)]), Wind.night = c(sol$x[(night+8760*2)]),Wind.late = c(sol$x[(late+8760*2)]) )

investments.df.com <- c(sol$x[(nTechnologies*nTimePeriods+1)],sol$x[(nTechnologies*nTimePeriods+2)],sol$x[(nTechnologies*nTimePeriods+3)])

generation.util.com <- sum(colSums(solution.df.com[1:6]))

cost.list.com[[i]] <- sol$objval
solution.list.com[[i]] <- solution.df.com
investments.list.com[[i]] <- investments.df.com
generation.util.list.com[[i]] <- generation.util.com


rm(sol,model,solution.df.com,investments.df.com,generation.util.com)
  

}


print('Objective Values for the Utility Models' )
unlist(cost.list)
print('Objective Values for the Community Models' )
unlist(cost.list.com)
print('Total Cost Utility+Community')
unlist(cost.list)+unlist(cost.list.com)*ncoms
print('Utility Prices')
lapply(price.demand.list,mean)
print('Utility Investments')
investments.list
print('Community Investments')
investments.list.com
print('Fraction of Energy Generation by Community')
(3000000-unlist(generation.util.list.com))*ncoms/(120000000)
print('Excess Electricity Produced by Community')
max(0,ncoms*sum(colSums(solution.list.com[[i]]))-(3000000*ncoms))
print('Mean $/kWh for Community Generation')
ncoms*unlist(cost.list.com) / (3000000*ncoms)


cost.list.10 <- cost.list
solution.list.10 <- solution.list
investments.list.10 <- investments.list
price.demand.list.10 <- price.demand.list

cost.list.com.10 <- cost.list.com
solution.list.com.10 <- solution.list.com
investments.list.com.10 <- investments.list.com


```

```{r}
#iterations for 20 communities
ncoms <- 20

params <- list(OutputFlag = 0)
for(i in 2:nitrs){
  
#New utility model with new demand

model <- model.util

demand.annual <- 3000000*(40-ncoms)+ncoms*generation.util.list.com[[(i-1)]]

model$rhs   <- c((demand.annual*demand.kwh[1:nTimePeriods]),rep(0,nrow(C2)))

sol <- gurobi(model, params)

solution.df <- data.frame(NG.early = c(sol$x[early]),NG.morning = c(sol$x[morning]), NG.noon = c(sol$x[noon]), NG.afternoon = c(sol$x[afternoon]), NG.night = c(sol$x[night]),NG.late = c(sol$x[late]), 
Solar.early = c(sol$x[(early+8760)]), Solar.morning = c(sol$x[(morning+8760)]), Solar.noon = c(sol$x[(noon+8760)]), Solar.afternoon = c(sol$x[(afternoon+8760)]), Solar.night = c(sol$x[(night+8760)]),Solar.late = c(sol$x[(late+8760)]), Wind.early = c(sol$x[(early+8760*2)]), Wind.morning = c(sol$x[(morning+8760*2)]), Wind.noon = c(sol$x[(noon+8760*2)]), Wind.afternoon = c(sol$x[(afternoon+8760*2)]), Wind.night = c(sol$x[(night+8760*2)]),Wind.late = c(sol$x[(late+8760*2)]) )


investments.df <- c(sol$x[(nTechnologies*nTimePeriods+1)],sol$x[(nTechnologies*nTimePeriods+2)],sol$x[(nTechnologies*nTimePeriods+3)])


#Tranmsission and Distribution cost $/kWh
price.fraction <-  (demand.kwh*demand.annual)/(investments.df[1]*CF[1:nTimePeriods]
                                                 +investments.df[2]*CF[(nTimePeriods+1):(nTimePeriods*2)]
                                                  +investments.df[3]*CF[(nTimePeriods*2+1):(nTimePeriods*3)])

price.fraction <- price.fraction/sum(price.fraction) 
price.demand <- price.fraction*sol$objval/(demand.annual*(demand.kwh+0.0000001))

cost.list[[i]] <- sol$objval
solution.list[[i]] <- solution.df
investments.list[[i]] <- investments.df
price.demand.list[[i]] <- price.demand


print(paste('Iteration Count:', i))

rm(sol,model,solution.df,investments.df,price.demand,price.fraction)


  
#New community model with new prices
model <- model.com

model$obj <- c(price.demand.list[[(i)]], rep((cost.variable.Solar+cost.td.com),nTimePeriods), rep((cost.variable.Wind+cost.td.com),nTimePeriods), 0, cost.annual.Solar, cost.annual.Wind)
sol <- gurobi(model,params)

solution.df.com <- data.frame(Util.early = c(sol$x[early]),Util.morning = c(sol$x[morning]), Util.noon = c(sol$x[noon]), Util.afternoon = c(sol$x[afternoon]), Util.night = c(sol$x[night]),Util.late = c(sol$x[late]), 
Solar.early = c(sol$x[(early+8760)]), Solar.morning = c(sol$x[(morning+8760)]), Solar.noon = c(sol$x[(noon+8760)]), Solar.afternoon = c(sol$x[(afternoon+8760)]), Solar.night = c(sol$x[(night+8760)]),Solar.late = c(sol$x[(late+8760)]), Wind.early = c(sol$x[(early+8760*2)]), Wind.morning = c(sol$x[(morning+8760*2)]), Wind.noon = c(sol$x[(noon+8760*2)]), Wind.afternoon = c(sol$x[(afternoon+8760*2)]), Wind.night = c(sol$x[(night+8760*2)]),Wind.late = c(sol$x[(late+8760*2)]) )

investments.df.com <- c(sol$x[(nTechnologies*nTimePeriods+1)],sol$x[(nTechnologies*nTimePeriods+2)],sol$x[(nTechnologies*nTimePeriods+3)])

generation.util.com <- sum(colSums(solution.df.com[1:6]))

cost.list.com[[i]] <- sol$objval
solution.list.com[[i]] <- solution.df.com
investments.list.com[[i]] <- investments.df.com
generation.util.list.com[[i]] <- generation.util.com


rm(sol,model,solution.df.com,investments.df.com,generation.util.com)
  

}

print('Objective Values for the Utility Models' )
unlist(cost.list)
print('Objective Values for the Community Models' )
unlist(cost.list.com)
print('Total Cost Utility+Community')
unlist(cost.list)+unlist(cost.list.com)*ncoms
print('Utility Prices')
lapply(price.demand.list,mean)
print('Utility Investments')
investments.list
print('Community Investments')
investments.list.com
print('Fraction of Energy Generation by Community')
(3000000-unlist(generation.util.list.com))*ncoms/(120000000)
print('Excess Electricity Produced by Community')
max(0,ncoms*sum(colSums(solution.list.com[[i]]))-(3000000*ncoms))
print('Mean $/kWh for Community Generation')
ncoms*unlist(cost.list.com) / (3000000*ncoms)


cost.list.20 <- cost.list
solution.list.20 <- solution.list
investments.list.20 <- investments.list
price.demand.list.20 <- price.demand.list

cost.list.com.20 <- cost.list.com
solution.list.com.20 <- solution.list.com
investments.list.com.20 <- investments.list.com


```

```{r}
#iterations for 30 communities
ncoms <- 30


params <- list(OutputFlag = 0)
for(i in 2:nitrs){
  
#New utility model with new demand

model <- model.util

demand.annual <- 3000000*(40-ncoms)+ncoms*generation.util.list.com[[(i-1)]]

model$rhs   <- c((demand.annual*demand.kwh[1:nTimePeriods]),rep(0,nrow(C2)))

sol <- gurobi(model, params)

solution.df <- data.frame(NG.early = c(sol$x[early]),NG.morning = c(sol$x[morning]), NG.noon = c(sol$x[noon]), NG.afternoon = c(sol$x[afternoon]), NG.night = c(sol$x[night]),NG.late = c(sol$x[late]), 
Solar.early = c(sol$x[(early+8760)]), Solar.morning = c(sol$x[(morning+8760)]), Solar.noon = c(sol$x[(noon+8760)]), Solar.afternoon = c(sol$x[(afternoon+8760)]), Solar.night = c(sol$x[(night+8760)]),Solar.late = c(sol$x[(late+8760)]), Wind.early = c(sol$x[(early+8760*2)]), Wind.morning = c(sol$x[(morning+8760*2)]), Wind.noon = c(sol$x[(noon+8760*2)]), Wind.afternoon = c(sol$x[(afternoon+8760*2)]), Wind.night = c(sol$x[(night+8760*2)]),Wind.late = c(sol$x[(late+8760*2)]) )


investments.df <- c(sol$x[(nTechnologies*nTimePeriods+1)],sol$x[(nTechnologies*nTimePeriods+2)],sol$x[(nTechnologies*nTimePeriods+3)])


#Tranmsission and Distribution cost $/kWh
price.fraction <-  (demand.kwh*demand.annual)/(investments.df[1]*CF[1:nTimePeriods]
                                                 +investments.df[2]*CF[(nTimePeriods+1):(nTimePeriods*2)]
                                                  +investments.df[3]*CF[(nTimePeriods*2+1):(nTimePeriods*3)])

price.fraction <- price.fraction/sum(price.fraction) 
price.demand <- price.fraction*sol$objval/(demand.annual*(demand.kwh+0.0000001))

cost.list[[i]] <- sol$objval
solution.list[[i]] <- solution.df
investments.list[[i]] <- investments.df
price.demand.list[[i]] <- price.demand


print(paste('Iteration Count:', i))

rm(sol,model,solution.df,investments.df,price.demand,price.fraction)


  
#New community model with new prices
model <- model.com

model$obj <- c(price.demand.list[[(i)]], rep((cost.variable.Solar+cost.td.com),nTimePeriods), rep((cost.variable.Wind+cost.td.com),nTimePeriods), 0, cost.annual.Solar, cost.annual.Wind)
sol <- gurobi(model,params)

solution.df.com <- data.frame(Util.early = c(sol$x[early]),Util.morning = c(sol$x[morning]), Util.noon = c(sol$x[noon]), Util.afternoon = c(sol$x[afternoon]), Util.night = c(sol$x[night]),Util.late = c(sol$x[late]), 
Solar.early = c(sol$x[(early+8760)]), Solar.morning = c(sol$x[(morning+8760)]), Solar.noon = c(sol$x[(noon+8760)]), Solar.afternoon = c(sol$x[(afternoon+8760)]), Solar.night = c(sol$x[(night+8760)]),Solar.late = c(sol$x[(late+8760)]), Wind.early = c(sol$x[(early+8760*2)]), Wind.morning = c(sol$x[(morning+8760*2)]), Wind.noon = c(sol$x[(noon+8760*2)]), Wind.afternoon = c(sol$x[(afternoon+8760*2)]), Wind.night = c(sol$x[(night+8760*2)]),Wind.late = c(sol$x[(late+8760*2)]) )

investments.df.com <- c(sol$x[(nTechnologies*nTimePeriods+1)],sol$x[(nTechnologies*nTimePeriods+2)],sol$x[(nTechnologies*nTimePeriods+3)])

generation.util.com <- sum(colSums(solution.df.com[1:6]))

cost.list.com[[i]] <- sol$objval
solution.list.com[[i]] <- solution.df.com
investments.list.com[[i]] <- investments.df.com
generation.util.list.com[[i]] <- generation.util.com


rm(sol,model,solution.df.com,investments.df.com,generation.util.com)
  

}


print('Objective Values for the Utility Models' )
unlist(cost.list)
print('Objective Values for the Community Models' )
unlist(cost.list.com)
print('Total Cost Utility+Community')
unlist(cost.list)+unlist(cost.list.com)*ncoms
print('Utility Prices')
lapply(price.demand.list,mean)
print('Utility Investments')
investments.list
print('Community Investments')
investments.list.com
print('Fraction of Energy Generation by Community')
(3000000-unlist(generation.util.list.com))*ncoms/(120000000)
print('Excess Electricity Produced by Community')
max(0,ncoms*sum(colSums(solution.list.com[[i]]))-(3000000*ncoms))
print('Mean $/kWh for Community Generation')
unlist(cost.list.com)*ncoms / (3000000*ncoms)


cost.list.30 <- cost.list
solution.list.30 <- solution.list
investments.list.30 <- investments.list
price.demand.list.30 <- price.demand.list

cost.list.com.30 <- cost.list.com
solution.list.com.30 <- solution.list.com
investments.list.com.30 <- investments.list.com


```

```{r}
#iterations for 40 communities
ncoms <- 40


params <- list(OutputFlag = 0)
for(i in 2:nitrs){
  
#New utility model with new demand

model <- model.util

demand.annual <- 3000000*(40-ncoms)+ncoms*generation.util.list.com[[(i-1)]]

model$rhs   <- c((demand.annual*demand.kwh[1:nTimePeriods]),rep(0,nrow(C2)))

sol <- gurobi(model, params)

solution.df <- data.frame(NG.early = c(sol$x[early]),NG.morning = c(sol$x[morning]), NG.noon = c(sol$x[noon]), NG.afternoon = c(sol$x[afternoon]), NG.night = c(sol$x[night]),NG.late = c(sol$x[late]), 
Solar.early = c(sol$x[(early+8760)]), Solar.morning = c(sol$x[(morning+8760)]), Solar.noon = c(sol$x[(noon+8760)]), Solar.afternoon = c(sol$x[(afternoon+8760)]), Solar.night = c(sol$x[(night+8760)]),Solar.late = c(sol$x[(late+8760)]), Wind.early = c(sol$x[(early+8760*2)]), Wind.morning = c(sol$x[(morning+8760*2)]), Wind.noon = c(sol$x[(noon+8760*2)]), Wind.afternoon = c(sol$x[(afternoon+8760*2)]), Wind.night = c(sol$x[(night+8760*2)]),Wind.late = c(sol$x[(late+8760*2)]) )

investments.df <- c(sol$x[(nTechnologies*nTimePeriods+1)],sol$x[(nTechnologies*nTimePeriods+2)],sol$x[(nTechnologies*nTimePeriods+3)])



#Tranmsission and Distribution cost $/kWh
price.fraction <-  (demand.kwh*demand.annual)/(investments.df[1]*CF[1:nTimePeriods]
                                                 +investments.df[2]*CF[(nTimePeriods+1):(nTimePeriods*2)]
                                                  +investments.df[3]*CF[(nTimePeriods*2+1):(nTimePeriods*3)])

price.fraction <- price.fraction/sum(price.fraction) 
price.demand <- price.fraction*sol$objval/(demand.annual*(demand.kwh+0.0000001))

cost.list[[i]] <- sol$objval
solution.list[[i]] <- solution.df
investments.list[[i]] <- investments.df
price.demand.list[[i]] <- price.demand


print(paste('Iteration Count:', i))

rm(sol,model,solution.df,investments.df,price.demand,price.fraction)


  
#New community model with new prices
model <- model.com

model$obj <- c(price.demand.list[[(i)]], rep((cost.variable.Solar+cost.td.com),nTimePeriods), rep((cost.variable.Wind+cost.td.com),nTimePeriods), 0, cost.annual.Solar, cost.annual.Wind)
sol <- gurobi(model,params)

solution.df.com <- data.frame(Util.early = c(sol$x[early]),Util.morning = c(sol$x[morning]), Util.noon = c(sol$x[noon]), Util.afternoon = c(sol$x[afternoon]), Util.night = c(sol$x[night]),Util.late = c(sol$x[late]), 
Solar.early = c(sol$x[(early+8760)]), Solar.morning = c(sol$x[(morning+8760)]), Solar.noon = c(sol$x[(noon+8760)]), Solar.afternoon = c(sol$x[(afternoon+8760)]), Solar.night = c(sol$x[(night+8760)]),Solar.late = c(sol$x[(late+8760)]), Wind.early = c(sol$x[(early+8760*2)]), Wind.morning = c(sol$x[(morning+8760*2)]), Wind.noon = c(sol$x[(noon+8760*2)]), Wind.afternoon = c(sol$x[(afternoon+8760*2)]), Wind.night = c(sol$x[(night+8760*2)]),Wind.late = c(sol$x[(late+8760*2)]) )

investments.df.com <- c(sol$x[(nTechnologies*nTimePeriods+1)],sol$x[(nTechnologies*nTimePeriods+2)],sol$x[(nTechnologies*nTimePeriods+3)])

generation.util.com <- sum(colSums(solution.df.com[1:6]))

cost.list.com[[i]] <- sol$objval
solution.list.com[[i]] <- solution.df.com
investments.list.com[[i]] <- investments.df.com
generation.util.list.com[[i]] <- generation.util.com


rm(sol,model,solution.df.com,investments.df.com,generation.util.com)
  

}


print('Objective Values for the Utility Models' )
unlist(cost.list)
print('Objective Values for the Community Models' )
unlist(cost.list.com)
print('Total Cost Utility+Community')
unlist(cost.list)+unlist(cost.list.com)*ncoms
print('Utility Prices')
lapply(price.demand.list,mean)
print('Utility Investments')
investments.list
print('Community Investments')
investments.list.com
print('Fraction of Energy Generation by Community')
(3000000*ncoms-unlist(generation.util.list.com))/(120000000)
print('Excess Electricity Produced by Community')
max(0,ncoms*sum(colSums(solution.list.com[[i]]))-(3000000*ncoms))
print('Mean $/kWh for Community Generation')
unlist(cost.list.com)*ncoms / (3000000*ncoms)


cost.list.40 <- cost.list
solution.list.40 <- solution.list
investments.list.40 <- investments.list
price.demand.list.40 <- price.demand.list

cost.list.com.40 <- cost.list.com
solution.list.com.40 <- solution.list.com
investments.list.com.40 <- investments.list.com


```

```{r}
#Create Solution Dataframe
nitrs <- 4
#already added to the cost so setting to zero for laziness
cost.td.com <- 0
cost.td <- 0

index.ng <- c()
index.solar <- c()
index.wind <- c()


for(i in 0:23){
index.ng <- c(index.ng,c(1,2,3,4,5,6)+i*18) 
index.solar <- c(index.solar,c(7,8,9,10,11,12)+i*18)
index.wind <- c(index.wind,c(13,14,15,16,17,18)+i*18)

}

production.util <- c((unlist(lapply(solution.list.1,colSums))),(unlist(lapply(solution.list.5,colSums))),(unlist(lapply(solution.list.10,colSums))),(unlist(lapply(solution.list.20,colSums))),(unlist(lapply(solution.list.30,colSums))),(unlist(lapply(solution.list.40,colSums))) )

production.ng.util <- round(production.util[index.ng]/1000000,3)
production.solar.util <- round(production.util[index.solar]/1000000,3)
production.wind.util <- round(production.util[index.wind]/1000000,3)

production.com <- c((unlist(lapply(solution.list.com.1,colSums))),(unlist(lapply(solution.list.com.5,colSums))),(unlist(lapply(solution.list.com.10,colSums))),(unlist(lapply(solution.list.com.20,colSums))),(unlist(lapply(solution.list.com.30,colSums))),(unlist(lapply(solution.list.com.40,colSums))) )

production.util.com <- round(production.com[index.ng]/1000000,3)
production.solar.com <- round(production.com[index.solar]/1000000,3)
production.wind.com <- round(production.com[index.wind]/1000000,3)

cost.util <- c((unlist(cost.list.1)+cost.td*unlist(lapply(lapply(solution.list.1,colSums),sum))),
               (unlist(cost.list.5)+cost.td*unlist(lapply(lapply(solution.list.5,colSums),sum))),
               (unlist(cost.list.10)+cost.td*unlist(lapply(lapply(solution.list.10,colSums),sum))),
               (unlist(cost.list.20)+cost.td*unlist(lapply(lapply(solution.list.20,colSums),sum))),
               (unlist(cost.list.30)+cost.td*unlist(lapply(lapply(solution.list.30,colSums),sum))),
               (unlist(cost.list.40)+cost.td*unlist(lapply(lapply(solution.list.40,colSums),sum))) )

cost.util <- round(cost.util / 1000000,3)

cost.com <- c((unlist(cost.list.com.1)),
               (unlist(cost.list.com.5)),
               (unlist(cost.list.com.10)),
               (unlist(cost.list.com.20)),
               (unlist(cost.list.com.30)),
               (unlist(cost.list.com.40)) )

cost.com <- round(cost.com / 1000000,3)

cost.total <- cost.util + c(cost.com[1:nitrs],cost.com[(nitrs+1):(nitrs*2)]*5,cost.com[(nitrs*2+1):(nitrs*3)]*10,cost.com[(nitrs*3+1):(nitrs*4)]*20,cost.com[(nitrs*4+1):(nitrs*5)]*30,cost.com[(nitrs*5+1):(nitrs*6)]*40)


price.util <- c(unlist(lapply(price.demand.list.1,mean)),unlist(lapply(price.demand.list.5,mean)),unlist(lapply(price.demand.list.10,mean)),unlist(lapply(price.demand.list.20,mean)),unlist(lapply(price.demand.list.30,mean)),unlist(lapply(price.demand.list.40,mean)))

price.com <- c((unlist(cost.list.com.1)*1 / (3000000*1) + cost.td.com),(unlist(cost.list.com.5)*5 / (3000000*5) + cost.td.com),(unlist(cost.list.com.10)*10 / (3000000*10) + cost.td.com),(unlist(cost.list.com.20)*20 / (3000000*20) + cost.td.com),(unlist(cost.list.com.30)*30 / (3000000*30) + cost.td.com),(unlist(cost.list.com.40)*40 / (3000000*40) + cost.td.com))

investment.ng.util <- c((unlist(lapply(investments.list.1,'[[',1))),(unlist(lapply(investments.list.5,'[[',1))),(unlist(lapply(investments.list.10,'[[',1))),(unlist(lapply(investments.list.20,'[[',1))),(unlist(lapply(investments.list.30,'[[',1))),(unlist(lapply(investments.list.40,'[[',1))) )

investment.solar.util <- c((unlist(lapply(investments.list.1,'[[',2))),(unlist(lapply(investments.list.5,'[[',2))),(unlist(lapply(investments.list.10,'[[',2))),(unlist(lapply(investments.list.20,'[[',2))),(unlist(lapply(investments.list.30,'[[',2))),(unlist(lapply(investments.list.40,'[[',2))) )

investment.wind.util <- c((unlist(lapply(investments.list.1,'[[',3))),(unlist(lapply(investments.list.5,'[[',3))),(unlist(lapply(investments.list.10,'[[',3))),(unlist(lapply(investments.list.20,'[[',3))),(unlist(lapply(investments.list.30,'[[',3))),(unlist(lapply(investments.list.40,'[[',3))) )

investment.solar.com <- c((unlist(lapply(investments.list.com.1,'[[',2))),(unlist(lapply(investments.list.com.5,'[[',2))),(unlist(lapply(investments.list.com.10,'[[',2))),(unlist(lapply(investments.list.com.20,'[[',2))),(unlist(lapply(investments.list.com.30,'[[',2))),(unlist(lapply(investments.list.com.40,'[[',2))) )

investment.solar.com <- round(investment.solar.com)

investment.wind.com <- c((unlist(lapply(investments.list.com.1,'[[',3))),(unlist(lapply(investments.list.com.5,'[[',3))),(unlist(lapply(investments.list.com.10,'[[',3))),(unlist(lapply(investments.list.com.20,'[[',3))),(unlist(lapply(investments.list.com.30,'[[',3))),(unlist(lapply(investments.list.com.40,'[[',3))) )

communities <- c(mapply(rep,c(01,05,10,20,30,40),nitrs))
communities <- as.factor(communities)

iteration <- rep(c(1:nitrs),6)


plotdf <- tibble(communities, iteration, cost.util,cost.com,cost.total,price.util,price.com,investment.ng.util,investment.solar.util,investment.wind.util,investment.solar.com,investment.wind.com)

communities <- c( mapply(rep,c(01,05,10,20,30,40),(6*nitrs)) )
communities <- as.factor(communities)

iteration <- rep(c( (mapply(rep,c(1:4),(6))) ), 6) 

timeofday <- rep(c('1-4 am','5-8 am','8am - 12pm ','12-4 pm','4-8 pm','8pm - 12am'),24)

plotdf.prod <- tibble(communities,iteration,timeofday,production.ng.util,production.solar.util,production.wind.util,production.util.com,production.solar.com,production.wind.com)

plotdf
plotdf.prod
```

```{r}
#cleanup

rm(afternoon,C2,CF,CF.com,cost.annual.NG,cost.annual.Solar,cost.annual.Wind,cost.com,cost.list,cost.list.com,cost.td,cost.td.com,cost.util,cost.variable.NG,cost.variable.Solar,cost.variable.Wind,early,generation.util.list.com,i,investments.list,investments.list.com,late,model.com,model.util,morning,ncoms,night,noon,nTechnologies,price.demand.list,solution.list,solution.list.com,Technologies,cost,demand.annual)
```

Organizes the data from all the scenarios and iterations and puts them in tidy format to be used later.












